\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Added Fotios to authors

\author{Séverin Lemaignan$^{1}$%
\thanks{$^{1}$Séverin Lemaignan is with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small severin.lemaignan@plymouth.ac.uk}}%
}

>>>>

\author{Séverin Lemaignan$^{1}$, Fotios Papadopoulos$^{1}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk}}%
}
